Visual Search and Pre-crastination

### 2023-09-01 RegReport/paper.tex
added pilot data, analysis and plots.

We collected data from a grand total of XXX participants. xxx of these participants failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. XXX participants completed the precrastination task (one participant was excused from this part of the experiment because of a brokem leg, and another for an unspecified reason). XXX participants completed the personality questionnaires (XXX participants had blank or otherwise unusable data).

>>>>

We collected data from a grand total of 305 participants. 14 of these participants had to be removed due to missing eyetracking data. Out of the 291 remaining, 90 failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. 303 participants completed the precrastination task (one participant was excused from this part of the experiment because of a brokem leg, and another for an unspecified reason). 304 participants completed the personality questionnaires (XXX participants had blank or otherwise unusable data).

### 2023-09-01 analysis/1_processing.Rmd
added pilot data, analysis and plots.

# read in fixation data (only first 20 fixations... see ascii files for full raw data)
dat_fix <- read_csv("../data/processed_fix_data.csv", col_types = "ddddddf")

@@

We have data from `r length(dat)/6` people and no missing data.

@@

```{r}
dat_p <- read_csv("../data/personality_q.csv")

>>>>

# read in fixation data (only first 20 fixations... see ascii files for full raw data)
dat_fix <- read_csv("../data/processed_fix_data.csv", col_types = "ddddddf")
```

Let's count participants:

```{r}
length(unique(dat_trl$person))
length(unique(dat_fix$person))
```

@@

We have data from `r nrow(dat)/6` people and no missing data.

@@

```{r, warning=FALSE, message=FALSE}
dat_p <- read_csv("../data/personality_q.csv") 
```

We have data from `r length(unique(dat_p$person))` people.

```{r}
